Countermeasures against co-location attempts in the cloud

### 2015-02-25 paper.tex
fix to one sentence per line
Added Motivation

To generate this pdf, you need a latex implementation. I recommend Texniccenter in Windows, but there are others. For your references (the .bib file) jabref is the only helpful editor I have used.
Refer to sections like this: Section~\ref{sec:background} and to references like this: Ristenpart et al.~\cite{Ristenpart_hey}. \\{\tiny There is also a word template available.}

We will stick to the following timeline:

\begin{itemize}
	\item 2/22: Project goals and outline defined
	\item 3/1 : Related work identified and described in report.
	\item 3/15: At least 1/3 of your anticipated work should be completed and documented
	\item 3/22: At least 2/3 of your anticipated work should be completed and documented
	\item 3/29: All of your anticipated work should be completed and documented
	\item 4/5:  Your results and outcomes are now also documented and included in the paper
	\item 4/12: Final submission of of complete paper for review
	\item 4/21: Reviews complete
	\item 4/26: Submission of final version addressing reviewers comments.
	\item 5/4 : Presentation of your project in class.
\end{itemize}

>>>>

\begin{itemize}
	\item Amazon's EC2 service is very popular and used for by variety of customers, some with sensitive data
	\item This makes VMs on this service a worthwhile target
	\item Ristenpart et. al have demonstrated that it is possible to create a VM co-resident with a target instance and
	that existing side-channel attacks can be employed against co-resident instances on the cloud
	\item We would like to focus on a method to obscure the algorithm by which instances are placed, which would make it
	significantly harder to achieve co-location
	\item Alternatively, we could focus on a method which prevents the simple network-based checks used to determine if two instances are co-located.

\end{itemize}
